---
title: "kickstarter"
author: "dayci"
date: "11/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
library(lubridate)
library(plotly)
library(ggplot2)
```

We hope to examine the following research questions:

2. What is the relationship between the goal ($) and the success of the campaign?
a. Distribution of (goal ($) - raised amount ($))
3. What is the relationship between a single pledge amount and goal (%)?
a. Do people pay more in expensive campaigns?
b. Do people pay differently in different countries?
4. How does the data vary across different categories of campaigns?
a. Which category has a higher success rate? (break down by countries) ?
b. Which categories have higher pledges/goals? Lower pledges/goals?

```{r}
df0 <- read.csv("ks-projects-201801.csv")
df0 %>% head()
```


```{r}
df <- df0 %>% 
  mutate(inicio = as.Date(df0$launched, format = "%Y-%m-%d"),
         final = as.Date(df0$deadline, format = "%Y-%m-%d"),
         duracion = as.numeric(final - inicio)) %>%
  filter(duracion <=365)
#max((df$duracion))
```

```{r}
hist(df$duracion)
boxplot(df$duracion ~ df$state)
```

```{r}
fig <- df %>%
  plot_ly(
    x = ~ state,
    y = ~ duracion,
    type = 'box',
    box = list(visible = T),
    meanline = list(visible = T)
  ) 
fig
```


```{r}
df <- df %>%
  filter(duracion <= 365)
```

```{r}
aov(duracion ~state, data = df)
```


```{r}


fig <- plot_ly(ggplot2::diamonds, y = ~ df$duracion, color = ~df$state, type = "box")
fig
```

### 1. Does the campaign length impact the success rate?

```{r}

```

